---
title: "Mapping the 2019 ATM"
author: "J. Dayton"
date: "5/28/2020"
output: html_document
always_allow_html: true
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(dplyr)
library(ggplot2)
library(ggmap)
library(kableExtra)
library(knitr)
library(lubridate)
library(trackeR)
```

### Background

As a continued relationship building event, my wife and I enjoy training for at least one 'official' run every year.  We started with 5k runs and this year we decided to embark on a 10-mile run.  These activities motivate us to perform physical activity ... together.  As part of Coursera's Developing Data Products course, I have decided to plot this years run, the Army Ten-Miler (ATM). (<https://www.armytenmiler.com/>)

### Data

Garmin is one of many fitness trackers on the market.  The data sensor utalized for colletion was a Garmin Forerunner 235 Smartwatch.  The event data from Garmin was download from my personal account through <https://connect.garmin.com>.  The personal activity data is automatically downloaded in 3 formats; .tcx, .gpx, and .kml.  The .tcx data was used for mapping this activity.
```{r getData}
##Load the data
dfRaw <- readTCX("./Garmin_Activity_Data/activity_4153631405.tcx")
```

#### Data Cleaning
There are three columns/variables, that do not contain data.  These three columns contained all NA values for the variables of _cadence_cycling_, _power_, and _temperature_.  Additionally, there are 9 data points (rows) that contain NA values for the latitude and longitude.  All NA values were removed for this analysis.
```{r setDF}
#Remove columns with NA Values
df <- dfRaw[, -c(9:11)]
#There are 9 rows with NA value in Lat and Lon
df <- df[!is.na(df$latitude), ] #Note:  The NA rows same for both lat and lon
```

#### Head of (Clean) Data Table
```{r datTab, warning=FALSE}
dTable <- kable(head(df), padding = 0, row.names = FALSE) %>%
   kable_styling(latex_options = c("striped", "scale_down"))
dTable
```
```{r getBaseMap, warning=FALSE, include=FALSE}
#Find the range of Lat and Lon
range(df$longitude)
range(df$latitude)

#Get the base map
base <- get_map(location = c(-77.085, 38.85, -77.01, 38.91), 
                maptype = "hybrid") #"hybrid" is likely googlemap
```
### Map of 2019 ATM Route
```{r firstPlot}
map1 <- ggmap(base) + 
   geom_point(data = df, aes(x = longitude, y = latitude), shape = 20, 
              color="red", cex = 0.25) +
   geom_label(x = df$longitude[1], y = df$latitude[1], position = "nudge", label = "Start/Finish", angle = 45, size = 2.5, color = "darkgreen") +
   labs(x="Latitude", y="Longitude", title="2019 Army Ten-Miler") + 
   theme_bw() 
map1
```

##### **_FIN_**