---
title: "Performance Information <br> My 2019 Army Ten-Miler"
author: "J. Dayton"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  ioslides_presentation: 
    widescreen: true
    smaller: true
  beamer_presentation: default
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(dplyr)
library(kableExtra)
library(knitr)
library(leaflet)
library(lubridate)
library(plotly)
library(RColorBrewer)
library(trackeR)

source("custFunc.R")
```

---
### Background

* As a continued relationship building event, my wife and I enjoy training for at least one 'official' run every year.  We started with 5k runs and this year we decided to embark on a 10-mile run.  These activities motivate us to perform physical activity ... together.  As part of Coursera's Developing Data Products course, I have decided to plot this years run, the Army Ten-Miler (ATM). (<https://www.armytenmiler.com/>)

### Data

* Garmin is one of many fitness trackers on the market.  The data sensor utalized for colletion was a Garmin Forerunner 235 Smartwatch.  The event data from Garmin was download from my personal account through <https://connect.garmin.com>.  The personal activity data is automatically downloaded in 3 formats; .tcx, .gpx, and .kml.  The .tcx data was used for mapping this activity.
```{r getData}
##Load the data
dfRaw <- readTCX("./Garmin_Activity_Data/activity_4153631405.tcx")
```

```{r setDF}
#Remove columns with NA Values
df <- dfRaw[, -c(9:11)]
rm(dfRaw)
#There are 9 rows with NA value in Lat and Lon
df <- df[!is.na(df$latitude), ] #Note:  The NA rows same for both lat and lon
```
```{r datTab, warning=FALSE, include=FALSE}
dTable <- kable(head(df), row.names = FALSE) 
dTable
```
```{r getBaseMap, warning=FALSE, include=FALSE}
#Find the range of Lat and Lon
range(df$longitude)
range(df$latitude)
```
## 2019 ATM Route (Leaflet Map)
```{r firstPlot}
#Leaflet with Markers
#Creating Marker Labels
labs <- lapply(seq(nrow(df)), function(i) {
   paste0( '<b>TIME: </b>', custTimeDiff(time1 = df$time[1], 
                                         time2 = df$time[i]), "</br>",
           '<b>DISTANCE: </b>',round((df[i, "distance"]/1609.34), 1), " mi</br>",
          '<b>HEART RATE: </b>',df[i, "heart_rate"], " bpm</br>",
          '<b>SPEED: </b>',round((df[i, "speed"]*2.2369), 2), " mph</br>",
          '<b>CADENCE: </b>',df[i, "cadence_running"], " bpm</br>",
          '<b>ALTITUDE: </b>',round(df[i, "altitude"], 2), " m" )
   
   
   } )
#Create Map
leafCircleMap <- df %>% 
   leaflet() %>% 
   addTiles() %>% 
   setView(lng = mean(df$longitude, na.rm = TRUE), 
           lat = mean(df$latitude, na.rm = TRUE),  
           zoom = 13) %>%
   addPolylines(lng = ~longitude, lat = ~latitude, color = "darkgreen", 
                weight = 4, opacity = 1 ) %>%
   addCircleMarkers(lng = df$longitude[1], lat = df$latitude[1], radius = 0,
    label = "START", labelOptions = labelOptions(noHide = T, 
                                                 direction = "left", 
                                                 offset = c(-4, 0),
                                                 style = list(
        "color" = "darkgreen",
        "font-family" = "arial",
        "font-style" = "italic",
        "box-shadow" = "1px 1px rgba(0,0,0,0.25)",
        "font-size" = "10px",
        "border-color" = "darkgreen"))) %>%
   addCircleMarkers(lng = df$longitude[length(df$longitude)], 
                    lat = df$latitude[length(df$latitude)], radius = 0,
    label = "FINISH", labelOptions = labelOptions(noHide = T, 
                                                 direction = "right", 
                                                 offset = c(4, 0),
                                                 style = list(
        "color" = "darkgreen",
        "font-family" = "arial",
        "font-style" = "italic",
        "box-shadow" = "1px 1px rgba(0,0,0,0.25)",
        "font-size" = "10px",
        "border-color" = "darkgreen"))) %>%
   addCircleMarkers(lng = ~longitude, lat = ~latitude,  
              color = "darkgreen", opacity = 0.9, radius = 0.1,
              label = lapply(labs, htmltools::HTML) )%>%
   addControl("<b>2019 ATM (13 October 2019)</b>", 
             position = "topright")
leafCircleMap
```

## Performance Plot (Plotly)
```{r plotPerformance}
#Update df to setup for plotting performance
df$elapsed <- custTimeDiff2(time = df$time)

#Create plot
fig <- df %>%
   plot_ly(x = ~elapsed, y = ~heart_rate,
             type = "scatter", mode = "markers",
             color = ~(-heart_rate), colors =  "RdYlGn", 
           
             hovertemplate = paste0("<i><b>Heat Rate:</b></i> ", "%{y}", " bpm <br>",
                                    "<i><b>Elapsed:</b></i> ", "%{x}","<extra></extra>"),
           showlegend = FALSE) %>%
   # hide_colorbar() %>%
   colorbar(title = "BPM") %>%
   layout(title="Performance:  Heart rate (BPM) over elapsed time", 
          xaxis = list(title = "Elapsed Time"),
          yaxis = list(title = "Heart Rate (BPM)")
          )
fig          
```

