---
title: "GEO_Code - Garmin Example"
author: "J. Dayton"
date: "5/13/2020"
output: pdf_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
library(ggmap)
library(knitr)
library(lubridate)
library(trackeR)

source("custFunc.R")
```

## Get the Garmin Activity Data

Garmin is one of manu fitness trackers on the market.  The event data from Garmin was download from my personal account.  Source of data <https://connect.garmin.com/modern/activity/4153631405>.

```{r getData}
##Load the data
dfRaw <- readTCX("./Garmin_Activity_Data/activity_4153631405.tcx")
```

## Clean Data

There are columns that do not contain data, all NA values.  Additionally, there are 9 data points (rows) that contain NA values for the latitude and longitude.  The NA values are removed.

```{r setDF}
#Remove columns with NA Values
df <- dfRaw[, -c(9:11)]
#There are 9 rows with NA value in Lat and Lon
df <- df[!is.na(df$latitude), ] #Note:  The NA rows same for both lat and lon
kable(head(df), format = "markdown", padding = 0)
```

## Find the range of Lat and Lon

```{r getBaseMap, echo=TRUE, warning=FALSE, include=FALSE}
range(df$longitude)
range(df$latitude)

base <- get_map(location = c(-77.085, 38.85, -77.01, 38.91), 
                maptype = "hybrid") #"hybrid" is likely googlemap
```

## Check out the base map

The 

``` {r plotBase}
map1 <- ggmap(base)
map1
```

```{r firstPlot}
map1 <- ggmap(base) + 
   geom_point(data = df, aes(x = longitude, y = latitude), shape = 20, 
              color="red", cex = 0.25) +
   geom_label(x = df$longitude[1], y = df$latitude[1], position = "nudge", label = "Start/Finish", angle = 45, size = 2.5, color = "darkgreen") +
   labs(x="Latitude", y="Longitude", title="2020 Army 10 Miler") + 
   theme_bw() 
map1
```

```{r baseMap2, warning=FALSE, include=FALSE}
base2 <- get_map(location = c(-77.085, 38.85, -77.01, 38.91), 
                maptype = "satellite")
```

```{r plotBaseMap2}
ggmap(base2)
```

```{r plotAgain}
map2 <- ggmap(base2) + 
   geom_point(data = df, aes(x = longitude, y = latitude), shape = 20, 
              color="red", cex = 0.25) +
   geom_label(x = df$longitude[1], y = df$latitude[1], position = "nudge", label = "Start/Finish", angle = 45, size = 2.5, color = "darkgreen") +
   labs(x="Latitude", y="Longitude", title="2020 Army 10 Miler") + 
   theme_bw() 
map2
```

FIN